---
title: "nrcs_map"
author: "Erin C Rooney"
date: "`r Sys.Date()`"
output: html_document
---
---
title: "Fairbanks Map"
author: "Erin C Rooney"
date: "2023-03-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Fairbanks Map

### this script uses data provided by  NCEAS Arctic Data Center training course
### Reproducible practices for Arctic Research Using R

derived from: Jared Kibele and Jeanette Clark. 2018. State of Alaska’s Salmon and People Regional Boundaries. Knowledge Network for Biocomplexity. doi:10.5063/F1125QWP.


```{r}
source("code/FTICR-0-packages.R")
library(sf)
library(leaflet)
library(scales)
library(ggmap)
library(grid)
library(ggsn)

```

```{r}

ak_regions = read_sf("NCEAS/ak_regions_simp.shp")
st_crs(ak_regions)

ak_regions_3338 =
  ak_regions %>%
  st_transform(crs = 3338)
st_crs(ak_regions_3338)


```

```{r}

site_gps = read.csv("rawdata/site_gps_nrcs.csv")

#pop = read.csv("NCEAS/alaska_population.csv")


site_gps_4326= st_as_sf(site_gps, 
                  coords = c('lng', 'lat'),
                  crs = 4326,
                  remove = F)


site_gps_3338 = st_transform(site_gps_4326, crs = 3338)

gps_joined = 
  st_join(site_gps_3338, ak_regions_3338, join = st_within)
head(gps_joined)



rivers_3338 = read_sf("NCEAS/ak_rivers_simp.shp")
st_crs(rivers_3338)

```

## Alaska plot

```{r}


ak_map_fig =
  ggplot()+
  geom_sf(data = ak_regions_3338, aes(), fill = "#ddbea9")+
    geom_sf(data = gps_joined, aes(x = lat, y = lng, fill = type, shape = type), #shape = 21, fill = "#ffb703", 
           color = "black", size = 4)+
  scale_fill_manual(values = c("#4c956c", "#f07167", "#0081a7"))+
  scale_shape_manual(values = c(21, 22, 24))+
    labs(y = " ", x = " ", fill = "", shape = "")+
  theme_minimal()+
   scalebar(ak_regions_3338, location = "bottomright", dist = 500, height = 0.05, transform = FALSE, model = "WGS84", dist_unit = "km", st.size = 3,
            border.size = 0.05)

ggsave("output/ak_map_fig_nrcs.png", plot = ak_map_fig, height = 9, width = 9)



```

